### 2017-11-09 manuscript.rmd
set ncores=1 for fitContinuous()

@@

	source( "functions.R" )

@@

	# Set system computational parameters
	cores = detectCores()
	if ( cores < 1 ) {
		cores = 1
	}
	set.seed( 23456 )

@@

	x = calibration_times$age[calibration_times$clade == "Hominini"]
	gene_trees_extended = mclapply( gene_trees_calibrated, extend_nhx, x=x, mc.cores=cores )
	gene_trees_extended %<>% add_pics_to_trees()
	nodes_extended_contrast = gene_trees_extended %>% summarize_contrasts()

	pairwise_extended_summary = 
			mclapply( gene_trees_extended, get_pairwise_summary, mc.cores=cores ) %>% 
			bind_rows()

>>>>

	source( "functions.R" )
	set.seed( 23456 )

@@

@@

@@
